---
title: "QC filtered sequencing reads"
author: "Evangelyn Sim"
date: "2/2/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```




## Introduction

In the GEO submission 3 processed files were uploaded. 

1. hrna_dev_mf_fulllen_se_strrev_q30.mx.all.fix_filt.csv
2. hrna_dev_mf_fulllen_se_strrev_q30.mx.all.MvsF.fix_filt.csv
3. hrna_dev_mf_fulllen_se_strrev_q30.mx.all_unfiltered.csv

They have been uploaded in the /output folder and will be used below to generate different figures.



### Used libraries and functions

```{r}
library(edgeR)
library(limma)
library(Glimma)
library(gplots)

```


### Count per million reads

```{r}

rm1 <- read.csv("/group/card2/Evangelyn_Sim/Transcriptome_chromatin_human/Sequencing_ATAC_RNA/GITHUB/Human_Development_RNAseq_bulk/output/hrna_dev_mf_fulllen_se_strrev_q30.mx.all.fix_filt.csv", row.names = 1)

info = read.delim("/group/card2/Evangelyn_Sim/Transcriptome_chromatin_human/Sequencing_ATAC_RNA/GITHUB/Human_Development_RNAseq_bulk/output/RNAseq_samplesheet.txt", header = TRUE, sep = "\t")

m = match(info$ID,names(rm1))
rm2 = rm1[,m]
rm1 = rm2

mycpm = cpm(rm1)

summary(mycpm)

x <- DGEList(rm1)

names(x)

logcountsx = cpm(x, log = T)
write.csv(logcountsx, file = "/group/card2/Evangelyn_Sim/Transcriptome_chromatin_human/Sequencing_ATAC_RNA/GITHUB/Human_Development_RNAseq_bulk/output/logCPM_hrna_dev_mf_fulllen_se_strrev_q30.mx.all.fix_filt.csv")

barplot(x$samples$lib.size, names=colnames(x), las=2, col = c("violetred4","darkgoldenrod2","tomato")[info$Group], main = "Library size")
boxplot(logcountsx, xlab="", ylab="Log2 counts per million", las=2, col = c("violetred4","darkgoldenrod2","tomato")[info$Group])
abline(h=median(logcountsx), col="navy")

```
